Adaptive Video Streaming with Optimized Bitstream Extraction and PID-based Quality Control

### 2015-11-30 tmm.tex
A version with all concerns addressed

The proposed solutions for bitstream extraction and quality control are combined together and result in a higher and smoother PSNR curve representing the final video quality perceived by the user.

@@

\subsection{Bitstream Extraction}

@@

In \cite{Amonou07}, Amonou et al. proposed a bitstream extraction framework based on the concept of \textit{Quality Layers}. This framework has been adopted by the SVC reference software, i.e., JSVM  \cite{JSVM}, and achieves better R-D performance compared with the basic extractor of JSVM. In Amonou's framework, a Quality Layer value, which reflects a packet's R-D impact, is calculated and used for R-D optimized bitstream extraction. The process of obtaining distortion impact of every packet is extremely time consuming, and the distortion estimation accuracy can also be further improved. So other distortion/error models were proposed to either reduce the computational complexity or improve the estimation accuracy. Sun et al. \cite{Sun09} and Maani et al. \cite{Maani09} constructed models to calculate distortion based on the drift propagation between frames. Sun et al.'s method is almost as good as JSVM in regard of performance, but has much reduced complexity. Maani et al.'s model can achieve better estimation accuracy than JSVM; however, since it is a training-based model, more computation is needed to get robust model parameters. Ramanathan et al. \cite{Ramanathan12} proposed their concept and calculation method of the ``Quality Metadata'' to signal and use in bitstream extraction. Yang et al. \cite{Yang13} proposed a method based-on simulated annealing to solve the bitstream extraction problem. In both methods, the accuracy of distortion estimation is the key of the performance.

@@

\subsection{Quality Control}

Quality control is the second problem we will address in this paper. The result of a quality control algorithm gives the suitable bitrate for current transmission, which is directly related to the change of video quality perceived by the user. In an SVC streaming system, the bitrate determined by the quality control algorithm is used as the constraint under which bitstream extraction is performed. Even in non-SVC streaming systems (DASH, for example), quality control is an important part that requires careful design.

@@

The following of this paper will present our solution for each of the problems in detail. The solutions then work together and serve as a solid foundation for a practical adaptive video streaming system. It should be noted that, in practical video streaming systems there are other issues that need to be addressed. One of them is occasional packet loss during transmission, which will cause decoding errors and corrupted images, resulting in degradation of video quality. However, in this paper we will focus on server-side adaptation and simply assume that no packet loss is occurred.

@@

\subsection{Linear Error Model for Quality Scalable Video}
\label{sec:model}

In H.264/AVC, the decoding process involves a linear feature described in \cite{Winken08}, neglecting any rounding, clipping, and deblocking filtering operation. According to this feature, the main steps in H.264/AVC coding -- prediction, transform and quantization -- are proximately linear operations, and the whole coding process can be expressed in a matrix format as follows:
\begin{equation}
\label{eq:linear}
s = {\rm\bf M} \cdot s + {\rm\bf T} \cdot c + p \: ,
\end{equation}
It means, the reconstructed samples of a GOP (Group of Pictures), denoted by $s$, can be viewed as a linear combination of previously reconstructed samples in the GOP, the residual samples, and a static predictor. In (\ref{eq:linear}), $c$ refers to the transform coefficient values and $p$ is a static predictor; ${\rm\bf M}$ and ${\rm\bf T}$ are square matrices such that the product ${\rm\bf M} \cdot s$ gives the MCP (Motion Compensated Prediction) signal and ${\rm\bf T} \cdot c$ gives the residual values. The actual values of ${\rm\bf M}$ depend on the selected macroblock types, reference indices and motion vectors, whereas the actual values of ${\rm\bf T}$ depend on the chosen QP (Quantization Parameter) values.

@@

\subsection{Error Vector Acquisition}

@@

\begin{figure}[h]
\centering
\includegraphics[width = 0.9\linewidth]{GOP-Structure.png}
\caption{Group of pictures (GOP) in SVC \label{fig:GOP_Structure}}
\end{figure}

@@

\subsection{Distortion Estimation and Model Verification}

@@

To verify the linear error model, we conduct an experiment where random combinations of enhancement packets are removed from a video bitstream, and the distortion estimated by the linear error model are compared with the actual distortion caused by the removal. The video stream has the same GOP structure and quality layers as illustrated in Fig. \ref{fig:GOP_Structure}. One comparison result for the sequence {\em Foreman} (only first 33 frames are used) is shown in Fig. \ref{fig:model_verification}. The horizontal axis stands for frame index, and the vertical axis for MSE measurement. The solid line represents the actual MSE of a frame, and the dot line shows the estimated MSE using our Linear Error Model. It can be seen that the two lines are very close to each other, which demonstrates the accuracy of the proposed model. Table \ref{tab:estimation-error} lists the distortion estimation error for different sequences and shows that the average error is only about 5\%.

\begin{figure}[h]
\centering
\includegraphics[width = 1.0\linewidth]{ModelVerification.png}
\caption{Comparison of actual and estimated distortion for sequence {\em Foreman} \label{fig:model_verification}}
\end{figure}

@@

\subsection{Priority Assignment and Bitstream Extraction}
\label{subsec:priority}

@@

\subsection{The No-Reference Case}
\label{subsec:noref}

@@

PID control \cite{PID}\cite{Astrom02} is a control loop feedback mechanism commonly used in industrial control systems. \textit{Process variable} and \textit{setpoint} are two core concepts in PID control. The process variable stands for the current status of the system. The setpoint is the target for this automatic control system to reach. The goal of PID control is to minimize the error between process variable and setpoint by adjusting system inputs. The controller output $u(t)$ is defined as follows:

@@

\subsection{Process Variable Selection}
\label{subsec:variable}

@@

\subsection{Model Formulation}
\label{subsec:model}

@@

This ratio-based model is more simple and effective for the chosen process variable and setpoint. And note that, since the controller output ($u_t$) is also a ratio, it should be used as a multiplier to manipulate the system input, i.e., the pushing data rate.

The whole process of this algorithm is described in Algorithm \ref{algo:control}. Compared to other scheduling strategies, this quality control algorithm has several advantages. First, this algorithm does not just rely on current packet delay or information at fixed time point, so quality change may occur at any proper time. Second, since the model has taken prediction into account, we can actually decide whether the bandwidth will be high or low enough for the quality level to change, thus avoiding video quality fluctuation. Third, in this algorithm it's not necessary to change one quality level at a time. This enables fast quality drop when bandwidth suddenly decreases and fast quality rise when system starts, resulting in a seamless experience.

@@

\subsection{Parameter Selection}
\label{subsec:parameter}

Ziegler--Nichols method \cite{Ziegler42} is used to tune $K_p$, $K_i$, and $K_d$ to obtain better performance of the PID control system. This method is performed by setting integral and derivative parameters to zero and then tuning $K_p$ to a value $K_u$ until output begins to oscillate with constant amplitude. Assuming the oscillation period is $T_u$, we set $K_p = 0.6K_u$, $K_i = 2K_u/T_u$, and $K_d = K_u \cdot T_u/8$. $K_p$, $K_i$, and $K_d$ are then normalized to get the final parameters. In the following experiments, parameters are chosen as $K_p = 0.22$, $K_i = 0.73$, $K_d = 0.05$ by this method. As with other control systems, PID parameters are a result of tunning and may not suit to all use cases. However, it should be noted that in the video quality control algorithm, only the data rate and the bandwidth are considered, not the video content. Therefore once the parameters are tuned they should apply well to different video streams.

@@

To implement our proposed adaptive streaming system requires the combination of the optimized bitstream extraction method and the PID-based quality control algorithm. The latter determines the current bitrate to follow the bandwidth change, and the former will ensure the sub-stream with the best possible quality is obtained and sent under that bitrate constraint. They work together to deliver best quality of service for the user. Choosing DSS as the implementation basis, we have integrated the proposed algorithms into it for the purpose of both research and application. In this section, we first present separate experiments to show the advantage of each proposed solution, and then give the result when they are combined together. Readers who are interested in the practical implementation and demonstration can visit the online video website http://www.7dlive.com for more information.

\subsection{Experiments for Bitstream Extraction}

@@

In our experiments, all test bitstreams are encoded with the JSVM encoder, where the standard hierarchical B coding structure and CABAC entropy coding are used. Each bitstream contains one base layer and one enhancement layer, with quantization parameters QP = 33 and QP = 27, respectively. The enhancement layer is further divided into 2 Medium Grain Scalability (MGS) layers by configuring the MGS vector to separate the transform coefficients into two groups (containing 4 and 12 coefficients respectively). For each test bitstream, ten bitrate points (one with all enhancement packets, one with only the base layer packets, and 8 points between) are chosen for extraction. For each bitrate point, the extraction is conducted using the bitstream extractors in JSVM, with and without \textit{Quality Layers} (denoted as JSVM QL and JSVM Basic, respectively), and the proposed method. The size of the optimization window in the proposed method is set to 4 GOPs, with a GOP size of 8. All of the eight SVC standard sequences with CIF resolution are considered at 30FPS and tested in our experiments.

The performance comparisons for City, Foreman, Harbour, and Soccer are shown in Fig. \ref{fig:extraction-performance}. It can be seen that the R-D curves of the proposed method are always on the top. For each sequence, the maximum and average PSNR gain through all 10 bitrate points are calculated and listed in Table \ref{tab:extraction-gain}, which shows that our extraction method can achieve a significant performance gain compared with JSVM Basic, and also performs better than JSVM QL. Table \ref{tab:extraction-gain} also lists results when optimization window is 6 GOPs, i.e., 48 frames. It is demonstrated that a larger window size can increase performance to some degree. However, it should be noted that, the practical system we propose does not use optimization window exceeding 32 frames, for the reason stated in the end of Sub-section \ref{subsec:priority}.

@@

We simulate network fluctuation by adjusting bandwidth around a certain level. We set this level from 400 to 1400 kbps to reflect different average bandwidth. All the experiments are conducted with DSS as the software platform, and the bandwidth simulation is implemented with NetLimiter 3 \cite{Netlimiter}. The baseline algorithm in the comparison refers to the packet delay feedback (PDF) algorithm in the original DSS.

@@

\subsection{Result of the Combined System}

After combining the two algorithms together, the proposed adaptive streaming system is able to deliver a higher and smoother video quality for the user. We compare the proposed system's performance with DSS that supports SVC but has its original quality control method and JSVM Basic bitstream extraction. The result for the test sequence Soccer is present in Fig. \ref{fig:fluctuation-psnr}. It shows the streamed video's PSNR change when available bandwidth fluctuates around certain values (400kbps, 600kbps, 800kbps and 1000kbps). The bandwidth conditions are simulated with NetLimiter and intense fluctuations are observed. It can be seen that, the proposed system performs better in that it has effectively avoided unnecessary quality drop (e.g., note the curve around time 350s in Fig. \ref{fig:Fluctuation-PSNR3} or 150s in Fig. \ref{fig:Fluctuation-PSNR4}) and been able to keep a relatively higher PSNR value (e.g., note the curve around time 450s in Fig. \ref{fig:Fluctuation-PSNR1} or 500s in Fig. \ref{fig:Fluctuation-PSNR2}). The average and variance value of PSNR is also calculated and present in Fig. \ref{fig:fluctuation-psnr}, showing clearly the proposed system's advantage. For instance, in Fig. \ref{fig:Fluctuation-PSNR3} where bandwidth fluctuates around 800kbps, the average PSNR delivered by the proposed system is 38.75dB, 0.83dB higher than that of the baseline system, and the PSNR variance is also reduced from 1.24 to 0.69, indicating a more smooth video quality change.

>>>>

The proposed solutions for bitstream extraction and quality control are combined together and result in a higher and smoother PSNR curve representing the final video quality delivered to the user.

@@

\subsection{Bitstream Extraction}
\label{subsec:analysis-extraction}

@@

In \cite{Amonou07}, Amonou et al. proposed a bitstream extraction framework based on the concept of \textit{Quality Layers}. This framework has been adopted by the SVC reference software, i.e., JSVM  \cite{JSVM}, and achieves better R-D performance compared with the basic extractor of JSVM. In Amonou's framework, a Quality Layer value, which reflects a packet's R-D impact, is calculated and used for R-D optimized bitstream extraction. The process of obtaining distortion impact of every packet is extremely time consuming, and the distortion estimation accuracy can also be further improved. So other distortion/error models were proposed to either reduce the computational complexity or improve the estimation accuracy. Sun et al. \cite{Sun09} and Maani et al. \cite{Maani09} constructed models to calculate distortion based on the drift propagation between frames. Sun et al.'s method is almost as good as JSVM in regard of performance, but has much reduced complexity. Maani et al.'s model can achieve better estimation accuracy than JSVM; however, since it is a training-based model, more computation is needed to get robust model parameters. Ramanathan et al. \cite{Ramanathan12} proposed their concept and calculation method of the ``Quality Metadata'' to signal and use in bitstream extraction. Yang et al. \cite{Yang13} proposed a method based-on simulated annealing to determine and assign priority values used in bitstream extraction. In both methods, the accuracy of distortion estimation is the key of the performance.

@@

\subsection{Quality Control}
\label{subsec:analysis-control}

Quality control is the second problem we will address in this paper. The result of a quality control algorithm gives the suitable bitrate for current transmission, which is directly related to the change of video quality delieverd the user. In an SVC streaming system, the bitrate determined by the quality control algorithm is used as the constraint under which bitstream extraction is performed. Even in non-SVC streaming systems (DASH, for example), quality control is an important part that requires careful design.

@@

The following of this paper will present our solution for each of the problems in detail. The solutions then work together and serve as a solid foundation for a practical adaptive video streaming system. It should be noted that, in practical video streaming systems there are other issues that need to be addressed. One of them is occasional packet loss during transmission, which will cause decoding errors and corrupted images, resulting in an significant degradation of video quality. How to avoid or even recover from packet loss/error is an important research topic that is popular in both networking and multimedia community. However, in this paper which focuses on server-side adaptation, packet loss is not handled and we simply assume that the video stream will be successfully delivered to the client.

@@

\subsection{Linear Error Model for Quality Scalable Video}
\label{subsec:linear-model}

In H.264/AVC, the decoding process involves a linear feature described in \cite{Winken08}, neglecting any rounding, clipping, and deblocking filtering operation. According to this feature, the main steps in H.264/AVC coding -- prediction, transform and quantization -- are proximately linear operations, and the whole coding process can be expressed in a matrix format as follows:
\begin{equation}
\label{eq:linear}
s = {\rm\bf M} \cdot s + {\rm\bf T} \cdot c + p \: ,
\end{equation}
It means, the reconstructed samples of a Group of Pictures (GOP), denoted by $s$, can be viewed as a linear combination of previously reconstructed samples in the GOP, the residual samples, and a static predictor. In (\ref{eq:linear}), $c$ refers to the transform coefficient values and $p$ is a static predictor; ${\rm\bf M}$ and ${\rm\bf T}$ are square matrices such that the product ${\rm\bf M} \cdot s$ gives the Motion Compensated Prediction (MCP) signal and ${\rm\bf T} \cdot c$ gives the residual values. The actual values of ${\rm\bf M}$ depend on the selected macroblock types, reference indices and motion vectors, whereas the actual values of ${\rm\bf T}$ depend on the chosen Quantization Parameter (QP) values.

@@

\subsection{Error Vector Acquisition}
\label{subsec:error-vector}

@@

\begin{figure}[h]
\centering
\includegraphics[width = 1.0\linewidth]{GOP-Structure.png}
\caption{Group of pictures (GOP) in SVC \label{fig:GOP_Structure}}
\end{figure}

@@

\subsection{Distortion Estimation and Model Verification}
\label{subsec:distortion-estimation}

@@

Before using the linear error model, we conduct an experiment to verify it. All bitstreams in the experiment are encoded with the JSVM encoder, where the same GOP structure as illustrated in Fig. \ref{fig:GOP_Structure} and CABAC entropy coding are used. Each bitstream contains one base layer and one enhancement layer, with QP = 33 and QP = 27, respectively. The enhancement layer is further divided into 2 Medium Grain Scalability (MGS) layers by configuring the MGS vector to separate the transform coefficients into two groups (containing 4 and 12 coefficients respectively). Random combinations of enhancement packets are removed from a video bitstream, and the distortion estimated by the linear error model are compared with the actual distortion caused by the removal. One comparison result for the test sequence {\em Foreman} (only first 33 frames are used) is shown in Fig. \ref{fig:model_verification}. The horizontal axis stands for frame index, and the vertical axis for MSE measurement. The solid line represents the actual distortion for the frames, and the dot line represents the distortion estimated by the proposed linear error model. It can be seen that the two lines are very close to each other, which demonstrates the accuracy of estimation using the proposed model. Estimation errors for all the eight SVC standard test sequences are listed in Table \ref{tab:estimation-error}, which shows that the average error is only about 5\%.

\begin{figure}[t]
\centering
\includegraphics[width = 1.0\linewidth]{ModelVerification.png}
\caption{Comparison of actual and estimated distortion for sequence {\em Foreman} \label{fig:model_verification}}
\end{figure}

@@

\subsection{Priority Assignment and Bitstream Extraction}
\label{subsec:priority-assign}

@@

\subsection{The No-Reference Case}
\label{subsec:noref-case}

@@

PID control \cite{PID}\cite{Astrom02} is a control loop feedback mechanism commonly used in industrial control systems. \textit{Process variable} and \textit{setpoint} are two core concepts in PID control. The process variable stands for the current status of the system. The setpoint is the target for this control system to reach. The goal of PID control is to minimize the error between process variable and setpoint by adjusting system inputs. The controller output $u(t)$ is defined as follows:

@@

\subsection{Process Variable Selection}
\label{subsec:process-variable}

@@

\subsection{Model Formulation}
\label{subsec:model-formulation}

@@

This ratio-based model is more simple and effective for the chosen process variable and setpoint. Moreover, in this model the controller output has intuitive meaning when the three parameters are normalized. It is easy to know that all of the three PID parts ($E_p^t$, $E_i^t$, $E_d^t$) are ratios with a value more or less than 1, and the controller output $u_t$ is a weighted average of the three ratios, with the three parameters as weights. Therefore the controller output is also a ratio value around 1, which reflects the relationship between the bitrate appropriate for bandwidth condition and the bitrate currently being used. In other words, if the output is larger than 1, then the controller has determined the bitrate should be increased accordingly, and vice versa. Use it as a multiplier to manipulate the bitrate currently being used, and we would be able to control the streaming system to match bandwidth condition.

The whole process of the proposed algorithm is described in Algorithm \ref{algo:control}. Compared to other scheduling strategies, this quality control algorithm has several advantages. First, this algorithm does not just rely on current packet delay or information at fixed time point, therefore quality change may occur at any proper time. Second, since the model has taken prediction into account, it is able to decide whether the bandwidth will be high or low enough for the quality level to change in the near future, thus avoiding video quality fluctuation. Third, in this algorithm it's not necessary to change one quality level at a time. This enables fast quality drop to avoid a latent playback pause when bandwidth suddenly decreases, and fast quality rise to provide better video as soon as possible when system starts, resulting in a seamless watching experience where the user can enjoy the video without stopping or waiting.

@@

\subsection{Parameter Selection}
\label{subsec:parameter-selection}

As with other PID control systems in the industry, the selection of the three parameters is implementation-dependent and most of the time manual tuning with trial and error is required to achieve optimal results. Knowing the impacts of each parameter is useful in the practice of parameter selection. Generally,  the proportional part in PID controller affects the system's stability. If the proportional gain $K_p$ is too high, the system can become unstable. However, a low $K_p$ would result in long rising time that makes the system response slowly. In addition to eliminating steady-state error, the integral term also accelerates the movement of the process towards setpoint, which means increasing $K_i$ can reduce rising time. However, since the integral part accumulates errors from the past, it can cause the present value to overshoot the setpoint value, and too much $K_i$ will lead to instability as well. This can be compensated by the derivative part, which predicts system behaviour and has the effect of reducing the overshoot, increasing the stability, and improving the settling time (time it takes to reach setpoint after a disturbance). The big problem with derivative part is that it is very sensitive to noise, therefore industrial practices indicates that derivative gain $K_d$ should always stay low.

For the proposed quality control algorithm, Ziegler--Nichols method \cite{Ziegler42} is used to select the parameters to obtain better performance. This method is performed by setting integral and derivative parameters to zero and then tuning $K_p$ to a value $K_u$ until output begins to oscillate with constant amplitude. Assuming the oscillation period is $T_u$, we set $K_p = 0.6K_u$, $K_i = 2K_u/T_u$, and $K_d = K_u \cdot T_u/8$. $K_p$, $K_i$, and $K_d$ are then normalized to get the final parameters. In the following experiments, parameters are chosen as $K_p = 0.22$, $K_i = 0.73$, $K_d = 0.05$ by this method.

In this work we simply use the standard Ziegler--Nichols method which already takes above impacts into consideration and produces acceptably good results. Adopting more sophisticated or automated techniques to further optimize the parameters will be done in the future. It should also be noted that, in the video quality control algorithm only the data rate and the bandwidth are relevant, not the video content. Therefore once the parameters are chosen they should apply well to different video streams.

@@

To implement our proposed adaptive streaming system requires the combination of the optimized bitstream extraction method and the PID-based quality control algorithm. The latter determines the current bitrate to follow the bandwidth change, and the former will ensure the sub-stream with the best possible quality is obtained and sent under that bitrate constraint. They work together to deliver best quality of service for the user. Choosing DSS as the implementation basis, we have integrated the proposed algorithms into it for the purpose of both research and application. The greedy-like algorithm present in \ref{subsec:priority-assign} is performed to determine priority values for all enhancement NALUs in an SVC bitstream. Then the priority values are injected into the bitstream, storing in the priority identifier field of the NALU header. When DSS streams this video, by checking this field it can extract a bitstream under certain bitrate determined by the PID-based quality control algorithm.

In this section, we first present separate experiments to show the advantage of each proposed solution, and then give the result when they are combined together. Readers who are interested in the practical implementation and demonstration can visit the online video website http://www.7dlive.com for more information.

\subsection{Experiments for Bitstream Extraction}
\label{subsec:exp-extraction}

@@

In our experiments, all test bitstreams are encoded as stated in sub-section \ref{subsec:distortion-estimation}. For each test bitstream, ten bitrate points (one with all enhancement packets, one with only the base layer packets, and 8 points between) are chosen for extraction. For each bitrate point, the extraction is conducted using the bitstream extractors in JSVM, with and without \textit{Quality Layers} (denoted as JSVM QL and JSVM Basic, respectively), and the proposed method. The size of the optimization window in the proposed method is 32 frames, i.e., 4 GOPs with a GOP size of 8. All of the eight SVC standard sequences with CIF resolution are considered at 30FPS and tested in our experiments.

The performance comparisons for City, Foreman, Harbour, and Soccer are shown in Fig. \ref{fig:extraction-performance}. It can be seen that the R-D curves of the proposed method are always on the top. For each sequence, the maximum and average PSNR gain through all 10 bitrate points are calculated and listed in Table \ref{tab:extraction-gain}, which shows that our extraction method can achieve a significant performance gain compared with JSVM Basic, and also performs better than JSVM QL. Table \ref{tab:extraction-gain} also lists results when optimization window is 48 frames, i.e., 6 GOPs. It is demonstrated that a larger window size can increase performance to some degree. However, it should be noted that, the practical system we propose does not use optimization window exceeding 32 frames, for the reason stated in the end of sub-section \ref{subsec:priority-assign}.

@@

We simulate network fluctuation by adjusting bandwidth around a certain level. We set this level from 400 to 1400 kbps to reflect different average bandwidth. The simulation is implemented with NetLimiter 3 \cite{Netlimiter}, where the bandwidth varies randomly with certain distribution and intense fluctuations are observed. The baseline algorithm in the comparison refers to the packet delay feedback (PDF) algorithm in the original DSS.

@@

\subsection{Result of the Combined System}
\label{subsec:exp-combined}

After combining the two algorithms together, the proposed adaptive streaming system is able to deliver a higher and smoother video quality for the user. We compare the proposed system's performance with DSS that supports SVC but has its original quality control method and JSVM Basic bitstream extraction. The result for the test sequence Soccer is present in Fig. \ref{fig:fluctuation-psnr}. It shows the streamed video's PSNR change when available bandwidth fluctuates around certain values (400kbps, 600kbps, 800kbps and 1000kbps). It can be seen that, the proposed system performs better in that it has effectively avoided unnecessary quality drop (e.g., note the curve around time 350s in Fig. \ref{fig:Fluctuation-PSNR3} or 150s in Fig. \ref{fig:Fluctuation-PSNR4}) and been able to keep a relatively higher PSNR value (e.g., note the curve around time 450s in Fig. \ref{fig:Fluctuation-PSNR1} or 500s in Fig. \ref{fig:Fluctuation-PSNR2}). The average and variance value of PSNR is also calculated and present in Fig. \ref{fig:fluctuation-psnr}, showing clearly the proposed system's advantage. For instance, in Fig. \ref{fig:Fluctuation-PSNR3} where bandwidth fluctuates around 800kbps, the average PSNR delivered by the proposed system is 38.75dB, 0.83dB higher than that of the baseline system, and the PSNR variance is also reduced from 1.24 to 0.69, indicating a more smooth video quality change.
